### 2012-09-01 sections/implementation/flow-query-intermediate-format.tex
* implementation   * flow query intermediate format     * json query disables the stages   * performance optimizations     * ignoring redundant aggregation requests     * lazy comparator evaluations     * early filtering     * early thread exits     * context-aware pipeline stages     * inline writes

>>>>

The \texttt{JSON} query can also trigger and disable the stages at runtime.
This means that one only has to supply the constructs that one wishes to use.
The constructs that are not defined in the \texttt{JSON} query are inferred by
the execution engine as a disable request. The execution engine uses disable
flags that are turned on when the \texttt{JSON} query is parsed. These flags
are used throughout the engine to only enable the requested functionality.
